---
output: rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# FitUltD

<!-- badges: start -->
<!-- badges: end -->

The goal of FitUltD is to fit data that can't be fitted with ordinary density functions

## Installation

You can install the released version of FitUltD from [CRAN](https://CRAN.R-project.org) with: 

install.packages("FitUltD")


## Example

This is a basic example which shows you how to fit a multimodal random variable:

```{r example}
library(FitUltD)
#random Variable
RV <- c(rnorm(73,189,12), rweibull(82,401,87), rgamma(90,40,19))
set.seed(31109)
FIT1 <- FDistUlt(RV, plot = TRUE, subplot = TRUE)

```

One of the available options is to show the distribution functions that passed the Anderson Darling and Kolmogorov Smirnov tests, as well as their p-value and the proportion of the total distribution.

```{r cars}
FIT1[[3]]

```

By setting `plot` and `subplot` arguments as `TRUE`, is possible to visualizate each distribution which forms the most accurrate model.

Real data distribution versus fitted model.

```{r pressure, echo = FALSE}
FIT1[[4]][[1]]
```

Distributions that forms the fitted model.

```{r plots-mult, echo = FALSE}
FIT1[[4]][[2]]
```

